doe-pkgs-analysis

### 2021-08-29 analysis/doe-pkgs-analysis.Rmd
Add heatmap.

This method results error, and only work with the edges only. However, even with the example data, the error stil occurs (may be the bug in the package?)

@@

set.seed(1234567)
plot(routes_igraph, edge.arrow.size = 0.2, layout = layout_with_graphopt)
```

@@

```{r}
routes_tidy <- routes_igraph %>% as_tbl_graph() %>%
  activate(edges)

@@

>>>>

Note: This method results error, and only works with the edges only. However, even with the example data, the error stil occurs (may be the bug in the package?)

@@

set.seed(1234567)
plot(routes_igraph, edge.arrow.size = 0.2, layout = layout_with_graphopt)
```
Notes: The label overlapped, it is hard to see the network

@@

```{r}
# create the input based on the igraph object
routes_tidy <- routes_igraph %>% as_tbl_graph() %>%
  activate(edges)

@@

# Network graph with all the packages in CRAN task view

```{r}
routes_igraph_full <- graph_from_data_frame(d = pkg_edges, vertices = pkg_nodes_full, directed = TRUE)

routes_tidy_full <- routes_igraph_full %>% as_tbl_graph() %>%
  activate(edges)

routes_tidy_full
```

```{r}
ggraph(routes_tidy_full, layout = "stress") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(1, 'mm')), 
                 end_cap = circle(1, 'mm')) + 
  geom_node_point() + 
  geom_node_text(aes(label = name), repel = TRUE, size = 2) +
  theme_graph()
```

Note: Hard to read. Hence, with all of the package in CRAN task view, I will make a heatmap instead.

```{r}
pkg.mat = get.adjacency(routes_igraph_full, sparse = FALSE)
heatmap(pkg.mat[,109:1],Rowv = NA, Colv = NA,scale="none")
```
